Distortion-corrected kernel density estimate on Riemannian manifolds

### 2022-09-30 paper/paper.Rmd
Add new figures

```{r tpoutliers, fig.align = 'center', out.width = "95%", fig.cap="Highest density region plots of four manifold learning embeddings of the twin peak data. Variable KDE preforms better in finding kernel structures with ISOMAP and LLE, and in locating outliers with t-SNE and UMAP.", echo = FALSE}
knitr::include_graphics("figures/Twin Peak2000_5levels_outliers_comparison_5ml_r0_5.png")
```

@@

```{r tpisomapden, fig.align = 'center', out.width = "95%", fig.cap="Scatterplot of true density and estimated density ranks of ISOMAP embedding for KDE with both variable and fixed bandwidth. DC-KDE shows a strong linear positive relationship.", echo = FALSE}
knitr::include_graphics("figures/Twin Peak2000_density_isomap_r0_5_rank_nocolor.png")
```

@@

```{r fivedisomapden, fig.align = 'center', out.width = "95%", fig.cap="Scatterplot of true density and estimated density of different embeddings for KDE with both variable and fixed bandwidth. The point shapes indicates the two Gaussian mixture components and the colors shows the distance to the kernel cores.", echo = FALSE}
knitr::include_graphics("figures/fived_density_comparison_4ml_riem20.png")
```

>>>>

```{r tpoutliers, fig.align = 'center', out.width = "95%", fig.cap="Highest density region plots of five manifold learning embeddings of the twin peaks data in each row. The top 20 outliers, hightlighted in black and indexed in blue text, are found by the true manifold density (left panel), DC-KDE (middle panel) and KDE (right panel). DC-KDE finds more true outliers than KDE in all five rows.", echo = FALSE}
knitr::include_graphics("figures/Twin Peak2000_5levels_outliers_comparison_5ml_r0_5.png")
```

@@

```{r tpisomapden, fig.align = 'center', out.width = "95%", fig.cap="Scatterplot of true density and estimated density ranks of ISOMAP embedding for DC-KDE and KDE, with colors indicating the absolute rank errors weighted by the sum of true and estimated ranks. DC-KDE shows a strong linear positive relationship with a higher rank correlation compared to KDE.", echo = FALSE}
# knitr::include_graphics("figures/Twin Peak2000_density_isomap_r0_5_rank_nocolor.png")
knitr::include_graphics("figures/Twin Peak2000_densityrank_comparison_isomap_radius8_r0_5_rankdistcol.png")
```

@@

```{r fivedisomapden, fig.align = 'center', out.width = "95%", fig.cap="Scatterplot of true density and estimated density of different embeddings for KDE with both variable and fixed bandwidth. The point shapes indicates the two Gaussian mixture components and the colors shows the distance to the kernel cores.", echo = FALSE}
# knitr::include_graphics("figures/fived_density_comparison_4ml_riem20.png")
knitr::include_graphics("figures/sim4d10000_density_comparison_4ml_riem1k200_rawdensity.png")
```
